Sex and Power: sexual dimorphism in trait variability and its eco-evolutionary and statistical implications

### 2020-04-21 scripts/MouseSexDiffApril20_2020.Rmd
kable clean up

```{r}
kable(metacombo) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All) 
```

@@

#adding male / female symbols for Figure 4B

@@

# Invidual table for heterogeneity across all traits
# kable(metacombohetero) %>%
 # kable_styling() %>%
  #scroll_box(width = "100%", height = "200px")

@@

## Heterogeneity Table and Plot
### Supplemental Table 4: "Heterogeneity within groups"
 SZ: missing a desciption so far.
```{r}
kable(heterog6) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```

>>>>

```{r}
kable(metacombo, digits = 3) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

overall2 <- bind_rows(Behaviour, Morphology, Metabolism, Physiology, Immunology, Hematology, Heart, Hearing, Eye, All)

```
### Supplemental Table 4_NEW
```{r}
kable(overall2, , digits = 3) %>%
 kable_styling() %>%
  scroll_box(width = "100%", height = "200px")

@@

#adding male / female symbols for Figure 4B
# additional packages for intergating male / female symbols in plot 4
library(png)
library(grid)

@@

# Invidual table for heterogeneity across all traits
# kable(metacombohetero,, digits = 3) %>%
 # kable_styling() %>%
  #scroll_box(width = "100%", height = "200px")

@@

## Heterogeneity Table and Plot
### Supplemental Table 4: "Heterogeneity within groups"
 SZ: missing a desciption so far.
```{r}
kable(heterog6, digits = 3) %>%
  kable_styling() %>%
  scroll_box(width = "100%", height = "200px")
```
